Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
Added figures and stuff to the paper

Polyphony means multiple simultaneous notes. Monophony means only a single note at a time. These terms carry slightly different meanings outside of automated transcription research.

@@

\subsection{Audio data}
Our training data comes from a large database of piano MIDI files. MIDI is a standard for specifying the controlling and playing of digital instruments. A MIDI specifies the instruments, notes, volumes and the other information needed to digitally synthesize(sp?) a song. MIDI files may specify a type of instrument but the exact sonic characteristics of the virtual instrument are defined by the synthesizer. That is, two identical midi files played with different sythnesizers may sound different.

@@

\subsection{SVM}

% use support vector machines to predict note presence or absence at 10ms time steps based on
\citet{poliner2006discriminative} first used short-time Fourier transforms were applied to the audio data.  Then,  87(they omit the highest note) one-versus-all (OVA) SVM classifiers were trained, one for each note.  The SVM's were then used to predict the test data, and HMM's were used for post-process smoothing.
% one vs all
% frequency partition

@@

\begin{figure*}[t]
\begin{center}
\subfigure[]{
\includegraphics[scale=.6]{stft-dictionary}
\label{fig:stftdict}
}
\subfigure[]{
\includegraphics[scale=.6]{cqt-dictionary}
\label{fig:cqtdict}
}
\end{center}
\caption{ Two W dictionary matrices computed for the supervised NMF method. Each column represents the spectral signature of a piano note. (a) The W dictionary matrix computed using an STFT. (b) The W dictionary matrix computed using constant Q transform.}
\end{figure*}

@@

We implemented a NMF transcription system. We used constructed our $W$ matrix by concatenating spectra from training recording. We tried both a standard STFT spectrogram and constant Q transform spectrogram. We use the normalizations proposed by \citet{niedermayer2008non}. After creating the $W$ matrix, we calculate the $H$ matrix using the previously-defined multiplicative update rule. The $H$ matrix is smoothed using a median filter and thresholded. [TODO: Results]

@@

The following table captures our evaluation of these methods. We expect these accuracy measures to be lower than they were reported in the original papers because we are using a smaller training dataset and not attempting to optimize the methods.

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
Sup. NMF & 30.4\% & 92.4 \\ \hline
AdaBoost & 42.5\% & 113.9 \\ \hline
\end{tabular}
\end{center}

@@

We achieved the best results with...

>>>>

Polyphony means multiple simultaneous notes. Mono-phony means only a single note at a time. These terms carry slightly different meanings outside of automated transcription research.

@@

\subsection{Audio data}
Our training data comes from a large database of piano MIDI files. MIDI is a standard for specifying the controlling and playing of digital instruments. A MIDI specifies the instruments, notes, volumes and the other information needed to digitally synthesize a song. MIDI files may specify a type of instrument but the exact sonic characteristics of the virtual instrument are defined by the synthesizer. That is, two identical midi files played with different sythnesizers may sound different.

@@

\subsection{SVM}
% use support vector machines to predict note presence or absence at 10ms time steps based on

\citet{poliner2006discriminative} first proposed applying support vector machines to piano transcription. Their system uses 87 SVM classifiers, one for each piano key (but omitting the highest piano key), that predicts if its note is present or absent given the frequency magnitudes at a given time step. The SVMs are trained in a one-versus-all fashion. To speed up training and testing, the input space of frequency magnitudes is partitioned into lower and higher frequencies for the lower note and higher note classifiers, respectively. Their paper also implements a hidden Markov model to smooth the raw outputs from the SVMs.

% one vs all
% frequency partition

@@

\begin{figure*}[t]
\begin{center}
\subfigure[]{
\includegraphics[scale=.6]{stft-dictionary}
\label{fig:stftdict}
}
\subfigure[]{
\includegraphics[scale=.6]{H-matrix}
\label{fig:H-matrix}
}
\end{center}
\caption{ Two W dictionary matrices computed for the supervised NMF method. Each column represents the spectral signature of a piano note. (a) The W dictionary matrix computed using an STFT. (b) The W dictionary matrix computed using constant Q transform.}
\end{figure*}

@@

We implemented a NMF transcription system. We used constructed our $W$ matrix by concatenating spectra from training recording. We tried both a standard STFT spectrogram and constant Q transform spectrogram. We use the normalizations proposed by \citet{niedermayer2008non}. After creating the $W$ matrix, we calculate the $H$ matrix using the previously-defined multiplicative update rule. The $H$ matrix is smoothed using a median filter and thresholded.

@@

Table \ref{table:ourevals} captures our evaluation of these methods. We expect these accuracy measures to be lower than they were reported in the original papers because we are using a smaller training dataset and not attempting to optimize the methods.

\begin{center}
\label{table:ourevals}
\begin{tabular}{|l|l|l|}
\hline

Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
Sup. NMF & 30.4\% & 92.4 \\ \hline
AdaBoost & 42.5\% & 113.9 \\ \hline

\end{tabular}

\end{center}

@@

We achieved the best accuracy with the SVM method with HMM smoothing from \citet{poliner2006discriminative}.
